\documentclass{article}
\usepackage{prerex}
\usepackage{parselines}
\usepackage{array}

\smash{\Huge}

\date{02.12.2015}

\begin{document}

\section{Noob - Secondary Persona}

\subsection{Demography:}
\begin{itemize}
 \item female
 \item 20 years old
 \item lives in Gotenburg, Sweden
 \item art student
 \item ADD HOBBY
\end{itemize}

\subsection{Behaviors:}
\begin{itemize}
\item unproblematic personality
\item usually liked by everyone
\item enjoys people's companies
\item likes to try new stuff from time to time
\item active on all social media channels

\end{itemize}

\subsection{Needs and Goals:}
\begin{itemize}
 \item being occupied
 \item making friends
 \item belonging to a part of a group
 \item likes the feeling of being included
 \item fears that she will end alone one day
 \item is annoyed by trolls and purposefully evil people
 \item likes to find a person to leech on to
\end{itemize}

\pagebreak

https://www.wikidata.org/wiki/User:fillWithUsername
\begin{quote}
"Fill with quote"
\end{quote}

Jamie is a -year old student trying to figure out what she wants in life. She's studying art right now but used to study archeology and before that architecture. Once she finds something she loves she usually sticks to it though but it doesn't always work on the first try. She is constantly scared to miss out on smth and thus tires out many things before settling. She just started editing on Wikipedia and so far really enjoys it. She likes the community and appreciates all the help she is getting. Also she has the feeling that what she's doing actually has a impact which is important to her. She has been to a women's open editing session in her hometown already where she met loads of nice women. She is not the most tech-savy person but quite clevers o she usually figures out how something works fairly fast. On the other hand she is so used to all this user-friendly tech now adays that it's hard to tell wether she's just generation internet or if she actually has a good understanding of technology.

\end{document}
