\documentclass{article}
\usepackage{prerex}
\usepackage{parselines}
\usepackage{array}

\smash{\Huge}

\date{11.11.2015}

\begin{document}

\section{Sceptic long-time editor - Primary Persona}

\subsection{Demography:}
\begin{itemize}
 \item female
 \item 36 years old
 \item lives in Heidelberg, Germany
 \item married
 \item studied veterinary madicine Uni Heidelberg
 \item lives in a single apartment in quite neighborhood
 \item works as a veterianrian at Uniklinik Heidelberg
 \item has two dogs
 \item apartment in city center
\end{itemize}

\subsection{Behaviors:}
\begin{itemize}
\item calm personality
\item very assertive
\item very sociable
\item pragmatic/ goal oriented
\item helper personality
\item spends a lot of time in forums answering users questions
\end{itemize}

\subsection{Needs and Goals:}
\begin{itemize}
 \item protecting animals
 \item spread awareness
 \item likes the feeling to be needed and help
 \item would like more regular working hours
 \item worries that her marriage might fall apart
 \item scared of failing at her job and thus hurting someone
\end{itemize}

\pagebreak

https://www.wikidata.org/wiki/User:fillWithUsername
\begin{quote}
"Fill with quote"
\end{quote}

Miriam is 36 year old veterinarian working at the University clinic of Heidelberg. She often has to work long shifts and sometimes also night shifts. Often when she comes home her husband is already asleep and so their marriage hasn't been very stable for a while. She's thinking of changing to a regular veterinarian's office so she can have normal working hours. She lives for her job because helping animals is what drives her. When she sees a suffering animal, that needs help, and is unable to resist. She tries to extend her knowledge of animals, their illnesses and their potential treatments to the outside world because she wants that as many animals as possible find help. That's the reason why she spends hours in forums, when she comes home from work, answering people's questions about their animals. A couple of years ago she discovered Wikipedia as a tool to also spread knowledge. When she started editing she found that many articles on animal illnesses were incomplete or entirely missing. Over the years she has written and edited 20+ articles hoping that someone will make use out of them. Most of her articles are rather scientific and thus often require an infobox. Miriam knows about Wikidata but has no idea how to integrate the information and no time to figure it out. Right now she always types everything by hand but she would appreciate the help of not having to do so by just integrating Wikidata's item. She also already encountered the situation where there was an english version of her article but she didn't know how to connect both of them. She often worries that people don't take care properly of their pets. She has seen many situations in her work where mistreat them without even them knowing it. 
She sometimes thinks about having kids, but the way her marriage is going she doesn't think that would be a good idea. She feels bad for not being home often and letting her marriage slip but she is incapable of giving up on her animal care. She is determined to make a difference, even when it is just one article at a time.
She loves her two dogs Lilo and Stitch. She tries to spend as much time with them as possible taking them for extensive walks as often as she can and taking them on her run every morning. 

\end{document}
